\section{Professional Background}

\subsection{Software Engineer | Tech Lead (2020 - Present)}

\textbf{Current Position}

* Develops Android (Java, Kotlin), C\#, and Python applications using various frameworks like Xamarin and Spring Boot.
* Integrates with AWS Lambda and DynamoDB using Terraform and Terragrunt.
* Builds components for other teams, including Android apps, C\# apps for Windows and Mac (Xamarin), and Java services with AWS integrations.
* Previously served as a Tech Lead for a team of 6, managing tasks, capacity, and internal company processes.

\textbf{Skills:} Android, Java, Spring Boot, Kotlin, Python, AWS, Lambda, DynamoDB, C\#, Xamarin, Terraform, KMM

\subsection{Android Developer at Softbuilder (2018 - 2020)}

* Developed several sales-focused Android apps.
* Customized base apps for different clients.
* Created an Android app for salespeople to search for products, add items to carts, close sales, and work offline.
* Developed a Python (Flask) backend for an internal business insights portal.

\textbf{Skills:} Android, Kotlin, Java, Python, Flask, HTML, CSS, JavaScript


\subsection{Android Developer at Fábrica 704 (2017 - 2018)}

* Developed an Android and PHP app for taxi drivers at an international airport.
* The app calculated fares based on predetermined distance ranges and printed receipts for customers.
* Developed a proof-of-concept for geofencing using Bluetooth beacons to track taxi locations.

\textbf{Skills:} Android, Cordova, PHP, Java, IoT

\subsection{Fullstack Developer (Freelancer) (2017)}

* Developed an Android app and Node.js backend for a food distributor's sales business.
* The app took orders from customers, sent them to the backend for processing, generated invoices, and printed tickets for the customers.

\textbf{Skills:} Android, Java, Node.js

\subsection{IT Support Technician at Freitas Varejo (2014 - 2016)}

* Internal support, network, and server setup.

\section{Others/Personal projects}